### 2020-06-18 README.Rmd
Done permutations

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)

@@

# Remove weird folds with no trees in them from viz above
bw_growth_df <- bw_growth_df %>%
  filter(!foldID %in% c(19, 23, 21, 17, 8, 19))
```

@@

```{r, eval = run_bw}
# Big Woods
bw_specs <- bw_growth_df %>% 
  get_model_specs(model_number = 3, species_notion = 'trait_group')
bw_specs
```

@@

```{r, eval = run_bw}
# Big Woods
if (!file.exists("focal_vs_comp_bw.Rdata")) {
  tic()
  focal_vs_comp_bw <- bw_growth_df %>% 
    create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
  toc()
  save(focal_vs_comp_bw, file = "focal_vs_comp_bw.Rdata")
} else {
  load("focal_vs_comp_bw.Rdata")
}
```

@@

```{r, eval = run_bw}
# Big Woods
bw_growth_df <- focal_vs_comp_bw %>% 
  predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model) %>% 
  right_join(bw_growth_df, by = c("focal_ID" = "treeID"))

@@

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
library(yardstick)
library(viridis)

@@

# Remove weird folds with no trees in them from viz above
bw_growth_df <- bw_growth_df %>%
  filter(!foldID %in% c(19, 23, 21, 17, 8, 19))

# Save original
bw_growth_df_orig <- bw_growth_df
```

@@

```{r, eval = run_bw}
# Big Woods
bw_specs <- bw_growth_df_orig %>% 
  get_model_specs(model_number = 3, species_notion = 'trait_group')
bw_specs
```

@@

```{r, eval = run_bw}
# Big Woods
if (!file.exists("focal_vs_comp_bw.Rdata")) {
  tic()
  focal_vs_comp_bw <- bw_growth_df_orig %>% 
    create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
  toc()
  save(focal_vs_comp_bw, file = "focal_vs_comp_bw.Rdata")
} else {
  load("focal_vs_comp_bw.Rdata")
}
```

@@

```{r, eval = run_bw}
# Big Woods
bw_growth_df <- focal_vs_comp_bw %>% 
  predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model) %>% 
  right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID"))

@@

```{r, eval = FALSE}
# Number of permutation shuffles:
num_shuffle <- 4

# Compute observed RMSE for all models, but only do permutation shuffling for
# models 3,6,9
model_numbers <- c(3)

# Save results here
run_time <- rep(0, length(model_numbers))
observed_RMSE <- rep(0, length(model_numbers))
observed_RMSE_CV <- rep(0, length(model_numbers))
shuffle_RMSE <- list()
shuffle_RMSE_CV <- list()

for(i in 1:length(model_numbers)){
  # Start clock
  tic()

  # Modeling and species stuff
  model_number <- model_numbers[i]
  bw_specs <- bw_growth_df %>% 
    get_model_specs(model_number = model_number, species_notion = 'trait_group')

  # Focal vs comp main dataframe for analysis
  # Computed earlier
  load("focal_vs_comp_bw.Rdata")

  # 1. Compute observed test statistic: RMSE with no cross-validation ----
  # Fit model (compute posterior parameters)
  bw_fit_model <- focal_vs_comp_bw %>% 
    fit_bayesian_model(model_specs = bw_specs)

  # Make predictions, compute and save RMSE, and reset
  observed_RMSE[i] <- focal_vs_comp_bw %>% 
    predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model) %>% 
    right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
    rmse(truth = growth, estimate = growth_hat) %>%
    pull(.estimate)

  # 2. Compute observed test statistic: RMSE with cross-validation ----
  observed_RMSE_CV[i] <- focal_vs_comp_bw %>%
    run_cv(model_specs = bw_specs, max_dist = max_dist, cv_grid = bw_cv_grid) %>% 
    right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
    rmse(truth = growth, estimate = growth_hat) %>%
    pull(.estimate)

  # 3. Permutation distribution: RMSE with no cross-validation ----
  # Only do permutation shuffling for models 3, 6, 9
  if(model_number %in% c(3, 6, 9)){
    # Compute num_shuffle permutation test statistics
    shuffle_RMSE[[i]] <- numeric(length = num_shuffle)

    for(j in 1:num_shuffle){
      # Fit model (compute posterior parameters) with shuffling
      bw_fit_model_shuffle <- focal_vs_comp_bw %>% 
        fit_bayesian_model(model_specs = bw_specs, run_shuffle = TRUE)

      # Make predictions, compute and save RMSE, and reset
      shuffle_RMSE[[i]][j] <- focal_vs_comp_bw %>% 
        predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model_shuffle) %>% 
        right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
        rmse(truth = growth, estimate = growth_hat) %>%
        pull(.estimate)
    }
  } else {
    shuffle_RMSE[[i]] <- NA
  }

  # 4. Permutation distribution: RMSE with cross-validation ----
  # Only do permutation shuffling for models 3, 6, 9
  if(model_number %in% c(3, 6, 9)){
    # Compute num_shuffle permutation test statistics
    shuffle_RMSE_CV[[i]] <- numeric(length = num_shuffle)

    # Compute num_shuffle permutation test statistics
    for(j in 1:num_shuffle){
      # Compute and save RMSE, and reset
      shuffle_RMSE_CV[[i]][j] <- focal_vs_comp_bw %>%
        run_cv(model_specs = bw_specs, max_dist = max_dist, cv_grid = bw_cv_grid, run_shuffle = TRUE) %>% 
        right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
        rmse(truth = growth, estimate = growth_hat) %>%
        pull(.estimate)

      # Status update
      str_c("Model ", model_numbers[i], ", shuffle with permutation ", j) %>% print()
    }
  } else {
    shuffle_RMSE_CV[[i]] <- NA
  }

  # 5. Stop clock and save
  clock <- toc(quiet = TRUE)
  run_time[i] <- clock$toc - clock$tic
}

model_comp_tbl <- tibble(
  model_number = model_numbers,
  run_time = run_time,
  observed_RMSE = observed_RMSE,
  observed_RMSE_CV = observed_RMSE_CV,
  shuffle_RMSE = shuffle_RMSE,
  shuffle_RMSE_CV = shuffle_RMSE_CV,
)

save(model_comp_tbl, file = "model_comp_tbl_4_shuffles.RData")
```

```{r}
load("model_comp_tbl_4_shuffles.RData")
model_comp <- bind_rows(
  model_comp_tbl %>% select(model_number, run_time, observed = observed_RMSE, shuffle = shuffle_RMSE) %>% mutate(CV = FALSE),
  model_comp_tbl %>% select(model_number, run_time, observed = observed_RMSE_CV, shuffle = shuffle_RMSE_CV) %>% mutate(CV = TRUE)
) %>%
  gather(type, RMSE, -c(model_number, run_time, CV)) %>%
  arrange(CV, model_number) %>%
  mutate(
    model_number = case_when(
      model_number == 3 ~ "1. Trait-based (6): lambda = 6 x 6",
      model_number == 6 ~ "2. Phylogenetic family (20): lambda = 20 x 20",
      model_number == 9 ~ "3. Actual species (36): lambda = 36 x 36"
    )
  )

model_comp_observed <- model_comp %>%
  filter(type == "observed") %>%
  unnest()
model_comp_shuffle <- model_comp %>%
  filter(type == "shuffle") %>%
  unnest()

xlab <- expression(paste('RMSE (cm ',y^{-1},')'))

ggplot() +
  geom_vline(data = model_comp_observed, aes(xintercept = RMSE, col = CV), linetype = "dashed", show.legend = F) +
  geom_histogram(data = model_comp_shuffle, aes(x = RMSE, fill = CV), bins = 200) +
  labs(fill = "Cross-validated?", x = xlab) +
  facet_wrap(~model_number, ncol = 1) +
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE)
```
